Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-11-30 paper/paper.tex
Clean up for submission

% to restate the propostions
%\usepackage{thmtools,thm-restate}

%\declaretheorem[name=Proposition,style=definition]{proposition}

@@

% \usepackage{showframe}

\makeatletter\@ifpackageloaded{showframe}{
    % show lines down the middle columns too
    % http://tex.stackexchange.com/questions/16199/test-if-a-package-or-package-option-is-loaded
\newlength\Fcolumnseprule\setlength\Fcolumnseprule{0.4pt}\def\@outputdblcol{%
  \if@firstcolumn\global \@firstcolumnfalse \global \setbox\@leftcolumn \box\@outputbox
  \else
    \global \@firstcolumntrue
    \setbox\@outputbox \vbox{\hb@xt@\textwidth{\hb@xt@\columnwidth{\box\@leftcolumn \hss}%
    \vrule \@width\Fcolumnseprule\hfil{\normalcolor\vrule \@width\columnseprule}
    \hfil\vrule \@width\Fcolumnseprule\hb@xt@\columnwidth {\box\@outputbox \hss}}}\@combinedblfloats\@outputpage
    \begingroup\@dblfloatplacement\@startdblcolumn\@whilesw\if@fcolmade \fi{\@outputpage\@startdblcolumn}\endgroup
  \fi
}}{}
\makeatother

\usetikzlibrary{decorations, decorations.pathreplacing, calc, backgrounds,shapes.misc}
%cross
\tikzset{cross/.style={cross out, draw=uofgcobalt, minimum size=2*(#1-\pgflinewidth), inner sep=0pt, outer sep=0pt},cross/.default={1.5mm}}

\definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
\definecolor{uofgpumpkin}{rgb}{1.0, 0.72549, 0.282353}
\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}

@@

\section{Domain Filtering using Degrees}\label{section:degreefiltering}

@@

\vspace{0.5cm}% Do not remove! Otherwise, the caption overlaps the algorithm due to algorithm2e and
% multicol[vlined] not being entirely happy with each other.

@@

\begin{figure}[h!]
    \centering
    \includegraphics*{gen-graph-which-k-by-family.pdf}
    \caption{The proportion of instances, in different families, which become satisfiable for
    increasing values of $k$. The ``larger'' instances are those where we can prove unsatisfiability for
    $k = 5$, whilst the gap between the top of the bar and the top of the graph is the fraction of
    instances where a timeout was reached for at least one value of $k$.}\label{figure:which-k}
\end{figure}

@@

% Other stuff to stick back in: example of paths of length 3, correlation heatmap

>>>>

@@

\usetikzlibrary{decorations, decorations.pathreplacing, calc}

@@

\section{Domain Filtering Using Degrees}\label{section:degreefiltering}

@@

\vspace{0.5cm}% Be careful if you remove this! Something weird happens where the caption overlaps
% the algorithm due to algorithm2e and multicol[vlined] not being entirely happy with each other.
% If you take this out, please check the space between the algorithm and the caption very very
% carefully.

@@

\begin{figure}[h!]% The ! is needed to avoid this being bumped forward a page
    \centering
    \includegraphics*{gen-graph-which-k-by-family.pdf}
    \caption{The proportion of instances, in different families, which become satisfiable for
    increasing values of $k$. The ``larger'' instances are those where we can prove unsatisfiability for
    $k = 5$, whilst the gap between the top of the bar and the top of the graph is the fraction of
    instances where a timeout was reached for at least one value of $k$.}\label{figure:which-k}
\end{figure}

@@
